%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                             Curriculum Vitae                               %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt,a4]{article}
\topmargin-2.0cm
\advance\oddsidemargin-2.2cm
\advance\evensidemargin-2.2cm
\textheight9.22in
\textwidth6.6in
\newcommand\bb[1]{\mbox{\em #1}}
\def\baselinestretch{1.2} % Line spread.

\usepackage{enumitem}
\usepackage{multicol}
\usepackage[svgnames]{xcolor}
\usepackage[prefix = sol]{xcolor-solarized} % Use solarized color.

\usepackage{fancyhdr}
\usepackage{hyperref}

\definecolor{gray}{rgb}{0.4,0.4,0.4}

\begin{document}

%\thispagestyle{empty}
%\pagestyle{plain}

\pagestyle{fancy}
\lhead{\textcolor{solbase1}{\it Cheng Chou\/}}
\rhead{\textcolor{solbase1}{\thepage/2}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\footnotesize \textcolor{solbase1}{}}

%\pagestyle{myheadings}
%\markboth{Sundar Iyer}{Sundar Iyer}

\vspace*{0.4cm}
\begin{center}
{\huge \bf \textcolor{solblue}{Cheng Chou}}
\vspace*{0.25cm}
\end{center}

%=========================================
\begin{tabbing}
\=xxxxxxxx\=xxxxxxxx\=xxxxxxxx\=\kill
\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}

University Rd, & Phone: +44 (0) 116 373 6288 \\
Astley Clarke Building 130, University of Leicester & Email: \texttt{cchou@le.ac.uk} \\
Leicester, UK LE1 7RH & Website: \href{https://chengchou.github.io}{\texttt{https://chengchou.github.io}} \\
\end{tabular*}
\end{tabbing}
\vspace*{0.2cm}
%==========================================
\hrule
\vspace{0.2cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Employment
\subsubsection*{\textcolor{solblue}{EMPLOYMENT}}
\begin{itemize}
  \item Lecturer (Assistant Professor) in Economics, University of Leicester. August 2016
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\subsubsection*{\textcolor{solblue}{EDUCATION}}
\begin{tabbing}
xxxx\=xxxxxxxx\=xxxxxxxx\=xxxxxxxx\=\kill
%\>\begin{tabular*}{6.1in}{lr}

\>\begin{tabular*}{0.9\linewidth}{l@{\extracolsep{\fill}}r}
University of Southern California & Los Angeles, US \\
Ph. D., Economics, Advisor: Geert Ridder  &  {\it August 2016}\\
 & \\

Peking University & Beijing, China \\
M. A., Economics & {\it July 2010}\\
 & \\

Hunan Normal University & Changsha, China \\
B. A., Economics & {\it July 2006}
\end{tabular*}
\end{tabbing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{\textcolor{solblue}{RESEARCH INTERESTS}}
%\hrule
%\vspace{0.2cm}

\begin{list}{}{}
  \item My research interests are econometrics, in particular microeconometrics, and its applications in labor economics and empirical industrial organization.
\end{list}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Working papers
\subsubsection*{\textcolor{solblue}{WORKING PAPERS}}
\begin{enumerate}
  \item \emph{Identification and Linear Estimation of General Dynamic Programming Discrete Choice Models}, July, 2016.
  \item \emph{Estimation of Identified Sets in Nonlinear Panel Data Models}, Aug, 2013.
  \item \emph{Econometrics of Buy-Price English Auctions}, Oct, 2010.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
\subsubsection*{\textcolor{solblue}{PUBLICATIONS}}
\begin{enumerate}
  \item ``Market Timing: Recent Development and a New Test'', {\it Economics Letters}, 2011, 111, 105--109. (with Chia-Shang J. Chu)
  \item ``Testing Independence of Two Autocorrelated Binary Time Series'', {\it Statistics and Probability Letters}, 2010, 80, 69-–75. (with Chia-Shang J. Chu)
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Seminars
\subsubsection*{\textcolor{solblue}{INVITED SEMINARS}}
\begin{itemize}
  \item UC Davis Economics Department and Agriculture Economics and Resource Department (May 2016)
  \item UC San Diego Economics Department (April 2016)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conference
\subsubsection*{\textcolor{solblue}{CONFERENCE TALKS}}
\begin{itemize}
  \item The 2016 Bristol Econometrics Workshop, Bristol, UK, July, 2016.
  \item The 2015 California Econometrics Conference, Los Angeles, US, September, 2015.
  \item The 2015 World Congress of Econometric Society, Montreal, Canada, August, 2015.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching
\subsubsection*{\textcolor{solblue}{TEACHING EXPERIENCE}}
\begin{itemize}
\item {\it Teaching Assistant.} ECON615: Applied Econometrics, Professor Cheng Hsiao, Fall  2013 and 2015, USC.\@
\item {\it Teaching Assistant.} ECON511: Econometric Methods, Professor Roger Moon, Spring 2013 and 2014, USC.\@
\item {\it Teaching Assistant.} ECON251: Microeconomics for Business, Lecturer Mohammad Safarzadeh, Spring 2012, USC.\@
\item {\it Teaching Assistant.} ECON501: Macroeconomic Analysis and Policy, Associate Professor Mark Moore, Spring 2012, USC.\@
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Honors
\subsubsection*{\textcolor{solblue}{ACADEMIC HONORS}}
\begin{itemize}
  \item The Best Third-Year Paper Award, Department of Economics, USC 2013
  \item The Best Second-Year Paper Award, Department of Economics, USC 2012
  \item College Graduate Merit Award, USC 2010
\end{itemize}

\end{document}